Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-10-17 docs/ms_sageAbundance.Rmd
updates ms with bw figures

Figures
-------
```{r figure_1_alt,dependson="plot-options", fig.cap="Location of the 2.5$\\times$5 kilometer study area in southwestern Wyoming and a snapshot of the percent cover data in 1984.", fig.height=6, eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/studyarea_map.png")
grid.raster(img)
```

@@

```{r figure_2,dependson="plot-options", fig.cap="Posterior distributions of climate covariates. The x-axis is the standardized coefficient value because we fit the model using standardized covariate values. Only cumulative precipitation at time t is important (shown in blue; 90% CI does not overlap zero).", fig.height=4, eval=T}
library(png)
library(grid)
img <- readPNG("../results/post_climate_covariates.png")
grid.raster(img)
```

@@

```{r figure_8,dependson="plot-options", fig.cap="Model forecasts under future climate for three IPCC emissions scenarios. Shaded regions show 90/% quantiles for simulations conducted using different sets of parameters from the MCMC output. Lines show mean trajectories.", eval=F}
library(png)
library(grid)
img <- readPNG("../results/temporal_forecast.png")
grid.raster(img)
```

>>>>

Figures
-------
```{r figure_1_alt,dependson="plot-options", fig.cap="Location of the 2.5 x 5 kilometer study area in southwestern Wyoming and a snapshot of the percent cover data in 1984.", fig.height=6, eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/studyarea_map.png")
grid.raster(img)
```

@@

```{r figure_2a,dependson="plot-options", fig.cap="GCM yearly weather projections for our climate covariates.", eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/weather_projections.png")
grid.raster(img)
```

```{r figure_2,dependson="plot-options", fig.cap="Posterior distributions of climate covariates. The x-axis is the standardized coefficient value because we fit the model using standardized covariate values. Only cumulative precipitation at time t is important (shown in dark grey; 90% CI does not overlap zero).", fig.height=4, eval=T}
library(png)
library(grid)
img <- readPNG("../results/post_climate_covariates.png")
grid.raster(img)
```

@@

```{r figure_8,dependson="plot-options", fig.cap="Model forecasts under future climate for three IPCC emissions scenarios. Shaded regions show 90/% quantiles for simulations conducted using different sets of parameters from the MCMC output. Lines show mean trajectories.", eval=T}
library(png)
library(grid)
img <- readPNG("../results/temporal_forecast.png")
grid.raster(img)
```
